Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
rewrite section 3

\section{\our: Sparse function-space represenation of neural networks}
\paragraph{GP in the dual parameters}
As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ found through the Bayesian update equation using  GP prior and likelihood function can be parameterized by $\valpha$ and $\vbeta$:
\begin{equation}  \label{eq:gp_pred}
 \mu(\vx_i)_\textrm{post} = \vk_{\vx i}^\top \valpha \quad \text{and} \quad
  \kappa(\mathbf{x}_i, \mathbf{x}_i')_\textrm{post} = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
\end{equation}
the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
\begin{equation}
\label{eq:dual_param}
\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
\end{equation}
%
The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods. In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior. At the same time, in \cite{adam2021dual, chang2020fast}, they showed this relationship for variational Gaussian processes where the above expectation is with respect to the approximate posterior from the variational approximation. The parameter $\alpha$ relates to non-Bayesian approaches, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}. The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. For more detail, see \citet{wilkinson2023bayes}, which shows the links between approximate inference methods and how they solve the \cref{eq:dual_param}.

@@

Our approach contrasts to \citet{immer2021improving}, which uses a subset of the full model to try to reduce complexity, a less principled approach to build a sparse model given it ignores the information in the dataset. It is important to highlight that the sparsifying process is independent of the approximate inference technique. The \cref{eq:dual_param} are from the neural network definition \cref{eq-empirical-risk}. More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments.

>>>>

\section{\our: Sparse function-space represenation of neural networks}
\paragraph{GP in the dual parameters}
As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the posterior process $f_{\textrm{post}}$ found through the Bayesian update equation using  GP prior and likelihood function can be parameterized by $\valpha$ and $\vbeta$:
\begin{equation}  \label{eq:gp_pred}
  \myexpect_{p(f_i \mid\vy)}[f_i]= \vk_{\vx i}^\top \valpha \quad \text{and} \quad
  \mathrm{Var}_{p(f\mid\vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
\end{equation}
the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{m \times m}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
\begin{equation}
\label{eq:dual_param}
\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
\end{equation}
%
The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods. In \citet{csato2002sparse}, they iteratively find dual variables setting them to log the expectation of the approximate posterior. At the same time, in \cite{adam2021dual, chang2020fast}, they showed this relationship for variational Gaussian processes where the above expectation is with respect to the approximate posterior from the variational approximation. The parameter $\alpha$ relates to non-Bayesian approaches, for example, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}. While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.

@@

Our approach contrasts to \citet{immer2021improving}, which uses a subset of the full model to try to reduce complexity, a less principled approach to build a sparse model given it ignores the information in the dataset. It is important to highlight that the sparsifying process is independent of the approximate inference technique. The \cref{eq:dual_param} are from the neural network definition \cref{eq-empirical-risk}. More complicated inference techniques, such as variational inference, could be used, but given its simplicity, we only need a trained neural network; we use a Laplace approximation in our experiments. Furthermore, our dual variable view of approximate inference means we do not need to resort to retraining a separate sparse GP model.
